---
title: "fars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  width= 68
)
options(width = 68, cli.unicode = FALSE, cli.width = 68)
```
# fars package

The **fars** package is a collection of functions that can be used to 
read, wrangle, and plot multiple years of state US National Highway Traffic Safety Administration Fatality Analysis Reporting System data. 

The fars is easy to download and install.

```{r setup, eval=FALSE}
install.packages("fars")
library(fars)
```

# Functions

The function *make_filename* is useful for quickly creating potential filenames
based on the year of the data. This is assuming that you have downloaded the 
data as `r paste0("accident_year.csv.bz2")`.
```{r name, eval=FALSE}
test_year <- make_filename(2010)
test_year
```

The function *fars_read* uses the filename to check for the existence of the 
.csv in the folder. This function will tell you if the file does not exist.
```{r read, eval=FALSE}
test_df <- fars_read(test_year)
```

The function *fars_read_years* takes a list of years and checks for associated data
in the location. If exists it will read in the data file, creating a dataframe 
consisting of month and year.
```{r years, eval=FALSE}
test_df <- fars_read_years(years)
```

To get summary data, use *fars_zummarize_years*.
```{r summary, eval=FALSE}
test_df <- fars_summarize_years(years)
```
Plot the accidents.
```{r, eval=FALSE}
fars_map_state(state.num,year)
```
